Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-03-16 paper/paper.tex
scattered lagunage fixes

% on chosing the threshold
The threshold $\tau$ is picked so, that the remaining \textit{``non-zero''} parameters
are within $\delta$ relative tolerance of their mean with high probability under the
approximate posterior $q_\theta(W)$. This ensures that stochastic parameters are sufficiently
concentrated around $\mu$, which are used as stand-in values for network weights $W$,
when it runs in inference mode. Since $W$ is $\real$- or a proper $\cplx$-Gaussian, the
random variable $
  \tfrac{k \lvert W - \mu \rvert^2}
        {\alpha \lvert \mu \rvert^2}
$ is $\chi^2_k$ distributed with $k=1$ ($\real$) or $2$ ($\cplx$).
%
For a generous $\delta = 50\%$ tolerance all values of $\log \alpha$ below $-2.5$ yield
at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$
to exclude noisy parameters and encourage higher sparsity, at the same time being aware
that $q_\theta$ is merely an approximation. In comparison, $\tau = 3$ is commonly used as
the threshold \citep{molchanov_variational_2017,kingma_variational_2015}.

@@

% mention the same experimental setup as in MNIST
Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart and
replicate each experiment only twice.
%
% describe the VGG16 model and its cplx-valued modification
The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers being
replaced by their $\cplx$-valued versions. To maintain comparability, we halve the filter
sizes of $\cplx$ model \citep{monning_evaluation_2018}.
%
Each network is trained stagewise for $20$, $40$,
and $20$ epochs on the full training split of $50k$ colour $32\times32$ images. We use
only raw colour features (\texttt{raw}). We apply random crop and horizontal flips as
data augmentation and use a learning rate scheduler in SGD, which scales the base learning
rate after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$,
respectively.

% draw some conclusions
Figure~\ref{fig:figure__cifar10__trade-off} shows that although the prior used in ARD method
offers slightly less compression, it makes up for it by equally slightly better accuracy.
Furthermore, the results imply that that the halved $\cplx$ network visibly underperforms
in comparison with its $\real$ counterpart, although in MNIST-like experiment $\cplx$-valued
network with the same inner feature dimensions performed on close to $\real$-valued, which
is half the size of the former.

@@

% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
musical compositions. Folowing \citet{trabelsi_deep_2017}, we use it for automatic music
transcription task and study the $1d$ VGG-like $\cplx$-convent proposed therein. Similarly to
the study, we downsample the audio from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels,
and hold-out the same validation and test splits. During each training epoch we sample $1000$
mini-batches of the remaining $321$ compositions, with each mini-batch comprised of a random
full window of $4096$ samples picked from each waveform and transformed from $\real$ to
$\cplx$ with $1d$ FFT. Annotation labels are taken at the mid-point of the window.

>>>>

% on chosing the threshold
The threshold $\tau$ is picked so, that the remaining \textit{``non-zero''} parameters
are within $\delta$ relative tolerance of their mean with high probability under the
approximate posterior $q_\theta(W)$. This ensures that stochastic parameters are sufficiently
concentrated around $\mu$, which are used as stand-in values for network weights $W$,
when it runs in inference mode. Since $W$ is $\real$- or a proper $\cplx$-Gaussian, the
random variable $
  \tfrac{k \lvert W - \mu \rvert^2}
        {\alpha \lvert \mu \rvert^2}
$ is $\chi^2_k$ distributed with $k=1$ ($\real$) or $2$ ($\cplx$).
%
For a generous tolerance $\delta = 50\%$ all values of $\log \alpha$ below $-2.5$ yield
at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$
to exclude noisy parameters and encourage higher sparsity, at the same time being aware
that $q_\theta$ is merely an approximation. In comparison, $\tau = 3$ is commonly used as
the threshold \citep{molchanov_variational_2017,kingma_variational_2015}.

@@

% mention the same experimental setup as in MNIST
Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart and
replicate each experiment only twice.
%
% describe the VGG16 model and its cplx-valued modification
The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers being
replaced by their $\cplx$-valued versions. We halve the sizes of intermediate layers in
$\cplx$ model to assess comparability \citep{monning_evaluation_2018}.
%
Each network is trained stagewise for $20$, $40$,
and $20$ epochs on the full training split of $50k$ colour $32\times32$ images. We use
only raw colour features (\texttt{raw}). We apply random crop and horizontal flips as
data augmentation and use a learning rate scheduler in SGD, which scales the base learning
rate after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$,
respectively.

% draw some conclusions
Figure~\ref{fig:figure__cifar10__trade-off} shows that although the prior used in ARD method
offers slightly less compression, it makes up for it by equally slightly better accuracy.
Furthermore, the results imply that that the halved $\cplx$ network visibly underperforms
in comparison with its $\real$ counterpart, although in MNIST-like experiment $\cplx$-valued
network with the same inner feature dimensions demonstrates trade-off very similar to
$\real$-network, which has half the number of real parameters than the former.

@@

% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
musical compositions. Folowing \citet{trabelsi_deep_2017}, we use it in automatic music
transcription task and study the $1d$ VGG-like $\cplx$-convent proposed therein. Similarly to
the study, we downsample the audio from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels,
and hold-out the same validation and test splits. During each training epoch we sample $1000$
mini-batches of the remaining $321$ compositions, with each mini-batch comprised of a random
full window of $4096$ samples picked from each waveform and transformed from $\real$ to
$\cplx$ with $1d$ FFT. Annotation labels are taken at the mid-point of the window.
